---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

The goal is to predict the genetic effects of accession genetic values in new trials based on gene-performance associations in training trials.

We will use each of the `GrainWeightPerHectare` trials as a separate test case.

For each of these trials, we will use data from other trials **from different locations** as the training data.

This script will set up the testing/training partitions.

We will do this for both `GrainWeightPerHectareCorrected`, `GrainWeightPerHectare` and for `DaysToFlowering`. We will start with each of the

For `DaysToFlowering` we will set up two training sets: 1) using the same training trials as for `GrainWeightPerHectare`, 2) using all other trials from different locations.

For each trait and each test trial, this script will set up the training data in a common format.

```{r}
library(data.table)
trial_info = read.csv('../../Phenotype_data/Trial_info.csv')
blups_deregressed = fread('../../Phenotype_data/blups_deregressed.csv',data.table=F)
```

Create datasets for `GrainWeightPerHectare`

```{r}
blups = subset(blups_deregressed,Trait == 'GrainWeightPerHectareCorrected')
trial_counts = table(blups$Experimento)
trial_counts = data.frame(Experimento = names(trial_counts),n = trial_counts,Localidad = trial_info$Localidad[match(names(trial_counts),trial_info$Experimento)],Localidad = trial_info$Classification[match(names(trial_counts),trial_info$Experimento)])
```
